Prediction of US Election in 2024

### 2024-11-03 paper/paper.qmd
update clean data script

```{r}
# plot graphof pct of two candidates in each state against time
ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = state)) +
  geom_point() +
  facet_wrap(~ candidate_name, scales = "free_y") +
  theme_minimal() +
  #theme(legend.position = "bottom") +
  labs(
    y = "pct",
    x = "end date",
    color = "state",
    title = "pct of Donald Trump and Kamala Harris in each states",
  )
unique(president_polls_cleaned_data$methodology)
```

>>>>

```{r}
base_plot <- ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
  theme_classic() +
  labs(y = "Candidate Support (%)", x = "Date") 
#+  scale_x_date(date_labels = "%b %Y")  # 设置 x 轴只显示月份和年份

# 绘制候选人支持率的点图和光滑线
base_plot + 
  geom_point() + 
  geom_smooth(se = FALSE) + 
  theme(legend.position = "bottom")
```

```{r}
# plot graph of pct of two candidates in each state against time
ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct
                                         #, color = state
                                         )
       ) +
  geom_point() +
  facet_wrap(~ candidate_name, scales = "free_y") +
  theme_minimal() +
  #theme(legend.position = "bottom") +
  labs(
    y = "pct",
    x = "end date",
    color = "state",
    title = "pct of Donald Trump and Kamala Harris in each states",
  )
```
